Article figures

### 2021-06-10 src/article_figures.Rmd
Fixed cost computation.
There was a problem with separation into males and females.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("economic_effect_functions.R")
library(knitr)
library(tidyverse)
save_figs = FALSE
fig_path="~/FRCBS/results-for-eba-paper/pdf"
```

@@

```{r}
#data_frames <- map(dummy2_ids, get_data_frame)
df2 <- df %>% select(Id, threshold6, threshold12)  # Get the optimal thresholds
```

```{r}
helper <- function(Id, threshold6, threshold12) {
  df2 <- get_data_frame(Id)
  r6 <- get_rates(df2, threshold6)
  r12 <- get_rates(df2, threshold12)
  df <- get_cost(r6$TPR, r6$FPR, r12$TPR, r12$FPR, p = parameters)
  #df <- tibble(a=1, b=2)
  df$Id <- Id
  return(df %>% select(Id, everything()))  
}

d <- get_mikkos_cost_constants()$d  # Fraction of deferrals of all donors
result <- pmap_dfr(df2, helper) 
result <- result %>%
  mutate(across(c(q6, q12), function(x) x / d)) %>%
  rename(Q6=q6, Q12=q12)
kable(result, digits=3)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("economic_effect_functions.R")
library(knitr)
library(tidyverse)
save_figs = FALSE
fig_path="~/FRCBS/results-for-eba-paper/pdf"
table_path="~/FRCBS/results-for-eba-paper/table"
```

@@

```{r, Get optimal thresholds}
#data_frames <- map(dummy2_ids, get_data_frame)
compute=TRUE
if (compute) {
  threshold_range <- seq(0.02, 0.98, 0.02)
  data_frames <- map(all_ids, get_data_frame)
  thresholds <- map2_dfr(data_frames, all_ids, function(df, id) get_optimal_thresholds(df, parameters, threshold_range, id)) %>%
    mutate(Id=all_ids) %>%
    select(Id, threshold6, threshold12)
} else {
  thresholds <- df %>% select(Id, threshold6, threshold12)  # Get the optimal thresholds
}
```

```{r}
helper <- function(Id, threshold6, threshold12) {
  df3 <- get_data_frame(Id)
  r6 <- get_rates(df3, threshold6)
  r12 <- get_rates(df3, threshold12)
  sex <- get_sex(Id)
  df <- get_cost(r6$TPR, r6$FPR, r12$TPR, r12$FPR, sex=sex, p = parameters)
  #df <- tibble(a=1, b=2)
  df$Id <- Id
  return(df %>% select(Id, everything()))  
}

d <- get_mikkos_cost_constants()$d  # Fraction of deferrals of all donors
result <- pmap_dfr(thresholds, helper) 
result <- result %>%
  mutate(across(c(q6, q12), function(x) x / d)) %>%
  inner_join(thresholds, by="Id")
  #rename(Q6=q6, Q12=q12)
kable(result, digits=3)
```

Get all variables and their confidence intervals

```{r}
  all_results <- process_all_data(all_ids)
  filename <- sprintf("%s/raw-data-2021-06-10.tsv", table_path)
  write_tsv(all_results, file=filename)
```
Same results in wide format xlsx
```{r}
library(openxlsx)
temp <- all_results %>% pivot_wider(names_from=c(variable, type))
filename <- sprintf("%s/pretty-data-2021-06-10.xlxs", table_path)
openxlsx::write.xlsx(temp, file = filename, overwrite=TRUE)
```

```{r}
g <- draw_surface(results=all_results %>% filter(Id == "progesa-both-rf"))
if (save_figs) {
  filename <- sprintf("%s/cme_cost_surface_werr.pdf", fig_path)
  ggsave(filename=filename,  width = 180,  height = 120, units="mm", dpi=600, scale=1.0, device=cairo_pdf)
}
g
```
